---
title: "Untitled"
author: "Caitie"
date: "2022-08-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(data.table)
library(countrycode)
library(raster)
library(sf)
library(ggplot2)
library(ggrepel)

t_crs<-'ESRI:54009'
```

# EEZ results

## Total sediment plumed

## EEZ Mismatch

```{r}
eez_mismatch<-read.csv(here("output_data/EEZ_sediments/EEZ_sed_trans_mismatch.csv"))
```

# Number of transboundary eez basins

```{r}
length(unique(eez_mismatch$MAIN_BAS))
```


```{r}
iso3_eez_mismatch<-eez_mismatch %>% 
  mutate(Sink_ISO3 = ifelse(Sink_ISO3 == " ", Sink_SOVISO3, Sink_ISO3)) %>% 
  group_by(Source_ISO3, Sink_ISO3) %>% 
  summarise(shared_sed = sum(total_eez_sed, na.rm = T),
            source_sed = sum(unique(Source_sediment), na.rm = T),
            prop = shared_sed/source_sed) %>% 
  dplyr::select(Source_ISO3, Sink_ISO3, shared_sed, source_sed, prop)
```

# Number of countries releasing sediment that is transboundary

```{r}
length(unique(iso3_eez_mismatch$Source_ISO3))
```

# Total sediment released from transboundary watersheds

```{r}
sum(iso3_eez_mismatch$source_sed)/1000000
```

# Total sediment released from pourpoints

```{r}
pp_sed<-st_read(here("output_data/Sediment_at_pourpoint/Sediment_at_pourpoint.gpkg")) #%>% 
  #dplyr::select(MAIN_RI, MAIN_BAS) %>% 
  #as.data.frame() %>% 
  #dplyr::select(-geom) %>% 
  #unique()
```
# Total sediment released at pourpoints

```{r}
 sum(pp_sed$sed_pp, na.rm = T)/1000000
```
# Proportion of sediment released from transboundary basins
```{r}
(sum(iso3_eez_mismatch$source_sed)/1000000)/(sum(pp_sed$sed_pp, na.rm = T)/1000000)
```

# Amount of sediment that ends up in another country

```{r}
sum(iso3_eez_mismatch$shared_sed, na.rm = T)/1000000
(sum(iso3_eez_mismatch$shared_sed, na.rm = T)/1000000)/(sum(iso3_eez_mismatch$source_sed)/1000000)
```

# Greatest sources of transboundary sediment

```{r}
source_eez_mismatch<- iso3_eez_mismatch %>% 
  group_by(Source_ISO3) %>% 
  summarise(shared_sed_source = sum(shared_sed, na.rm = T),
            total_sed_source = sum(source_sed, na.rm = T),
            n_sinks = length(unique(Sink_ISO3)),
            prop_shared = shared_sed_source/total_sed_source)

source_eez_mismatch<-source_eez_mismatch %>% 
  mutate(prop_total = shared_sed_source/sum(source_eez_mismatch$shared_sed_source))

```

```{r}
test<-source_eez_mismatch %>% 
  filter(n_sinks >=7)

sum(test$shared_sed_source, na.rm = T)/sum(source_eez_mismatch$shared_sed_source)
sum(test$total_sed_source, na.rm = T)/sum(source_eez_mismatch$total_sed_source)
```

```{r}
ggplot(source_eez_mismatch, aes(y = log10(shared_sed_source/1000000+1) , x = log10(total_sed_source/1000000+1), colour = n_sinks, label = Source_ISO3)) +
  geom_point() +
  geom_text_repel() +
  theme_bw()
```


```{r}
sink_eez_mismatch<- iso3_eez_mismatch %>% 
  group_by(Sink_ISO3) %>% 
  summarise(shared_sed_sink = sum(shared_sed, na.rm = T),
            n_sources = length(unique(Source_ISO3)))

sink_eez_mismatch<-sink_eez_mismatch %>% 
  mutate(prop_total = shared_sed_sink/sum(sink_eez_mismatch$shared_sed_sink))
```

# Number of countries that a country exports or imports sediment from




# Country that has overlap with multiple countries

# Countries that trade sediment back and forth

```{r}
all<-read.csv(here("output_data/EEZ_sediments/Country_sediment_exchange_results.csv"))
```

# Countries that receive more sediment than they produce themselves


```{r}
pp_sed_df<-pp_sed %>% 
  as.data.frame() %>% 
  dplyr::select(-geom) %>% 
  group_by(ISO3) %>% 
  summarise(total_sed_iso3 = sum(sed_pp, na.rm = T))
```

```{r}
prod_sink_mismatch<-full_join(pp_sed_df, sink_eez_mismatch, by = c("ISO3" = "Sink_ISO3")) %>% 
  filter(!is.na(shared_sed_sink) == T)

sub_prod_sink<-prod_sink_mismatch %>% 
  filter(shared_sed_sink>total_sed_iso3) %>% 
  mutate(Country = countrycode(ISO3, "iso3c", "country.name"),
         shared_sed_mt = shared_sed_sink/1000000,
         total_sed_mt = total_sed_iso3/1000000,
         prop_mismatch = shared_sed_mt/total_sed_mt)
```


# Which transboundary EEZ basins are also transboundary terrestrial?

```{r}
eez_basins<-unique(eez_mismatch$MAIN_BAS)

basin_table<-read.csv(here("results/Basin_results_table.csv"))

trans_basins<-basin_table %>% 
  filter(n_iso3>1)

sub_eez_basins<-trans_basins %>% 
  filter(MAIN_BAS %in% eez_basins)

length(unique(sub_eez_basins$MAIN_BAS))

```

```{r}
list_prop_basin<-list.files(here("output_data"), pattern = "Prop_basin_iso3", full.names = TRUE)

sub_prop_basin<-list_prop_basin[grep(list_prop_basin, pattern = ".csv")] 

dat <- 
  do.call(rbind,
          lapply(sub_prop_basin, read.csv))

dat2<- dat %>% 
  filter(MAIN_BAS %in% sub_eez_basins$MAIN_BAS)
```
# Look at Angola and Namibia watersheds
```{r}
angola<-dat2 %>% 
  filter(MAIN_BAS == 1080020040)

namibia<-dat2 %>% 
  filter(MAIN_BAS == 1080015850)
```

```{r}
shp_files<-list.files(path = here("output_data/Sediment"), pattern = ".shp", full.names = T)

sed_dat<-do.call(rbind,
          lapply(shp_files, st_read)) %>% 
  st_transform(., t_crs) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)
```

```{r}
angola_sed<-sed_dat %>% 
  filter(MAIN_BAS == 1080020040)

sum_angola<-sum(angola_sed$sed_sum)

angola_sed<-angola_sed %>% 
  mutate(prop_sed = sed_sum/sum_angola)
```

```{r}
namibia_sed<-sed_dat %>% 
  filter(MAIN_BAS %in% c(1080015850))

sum_namibia<-sum(namibia_sed$sed_sum)

namibia_sed<-namibia_sed %>% 
  mutate(prop_sed = sed_sum/sum_namibia)
```

