---
title: "Untitled"
author: "Caitie"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("tidytuesdayR")
library(ggnetwork)
#devtools::install_github("yixuan/sysfonts")
library(sysfonts)
library(showtext)
library(raster)
library(grid)
library(gridExtra)
library(tidyverse)
library(sp)
library(rworldmap)
library(sf)
library(rgeos)
library(countrycode)
```
# Load data

```{r}
tuesdata <- tidytuesdayR::tt_load('2022-05-17')
tuesdata <- tidytuesdayR::tt_load(2022, week = 20)

eurovision <- tuesdata$eurovision

votes <- tuesdata$`eurovision-votes`
```
# Import Rubik font from Google

```{r}
font_add_google("Rubik", "Rubik")
showtext_auto()
```

# Tidy data
```{r}
# tidy country names, remove those not to be used, and those with fewer than 10 occurrences
vote_tidy <- votes %>%
  mutate(to_country = gsub("The Netherlands", "Netherlands", to_country),
         from_country = gsub("The Netherlands", "Netherlands", from_country)) %>%
  filter(semi_final == "f", jury_or_televoting == "J", is.na(duplicate) == TRUE, !(to_country %in% c()), !(from_country %in% c())) %>%
  mutate(both_country = paste0(pmin(to_country, from_country), pmax(to_country, from_country))) %>%
  group_by(both_country) %>%
  mutate(n = n(),
            points = mean(points)) %>%
  mutate(points = ifelse(n >= 10, points, 0)) %>%
  dplyr::select(to_country, from_country, both_country, points) %>%
  distinct()

vote_tidy <- vote_tidy %>%
  filter(from_country %in% vote_tidy$to_country) %>% 
  mutate(to_iso3 = countrycode(to_country, "country.name", "iso3c"),
         from_iso3 = countrycode(from_country, "country.name", "iso3c")) 

vote_tidy<- vote_tidy %>% 
  filter(is.na(to_iso3) == F,
         is.na(from_iso3) == F)
```

# Get country lat/long centroids

```{r}
# get world map
wmap <- getMap(resolution="high")

# get centroids
centroids <- gCentroid(wmap, byid=TRUE)

# get a data.frame with centroids
df <- as.data.frame(centroids)

# convert row names into first column
df <- tibble::rownames_to_column(df, "Country")

# Add in ISO3 codes
df <- df %>% 
  mutate(iso3 = countrycode(Country, "country.name", "iso3c")) %>% 
  filter(is.na(iso3) == F) # remove countries without iso3 for now
```

# Join vote data with country data
```{r}
eurovis_countries <- data.frame(iso3 = c(unique(vote_tidy$to_iso3))) %>%
  inner_join(df, by = c("iso3"))
```

# filter out countries that only appear in one column
```{r}
vote_filt <- vote_tidy %>%
  filter(from_iso3 %in% eurovis_countries$iso3 & to_iso3 %in% eurovis_countries$iso3) 
```

# pivot data into matrix format
```{r}
vote_mat <- vote_filt %>%
  select(-both_country) %>%
  pivot_wider(id_cols = to_iso3, names_from = from_iso3, values_from = points) %>%
  column_to_rownames(var="to_iso3")
```
```{r}
# replace NA with 0
vote_mat[is.na(vote_mat)] <- 0

# create matrix
vote_mat <- as.matrix(vote_mat)
```

# find mean points given both ways between countries
```{r}
 
vote_summ <- vote_filt %>%
  mutate(both_country = paste0(pmin(to_iso3, from_iso3), pmax(to_iso3, from_iso3))) %>%
  group_by(both_country) %>%
  summarise(points = mean(points, na.rm = TRUE),
            from_country = first(from_iso3),
            to_country = first(to_iso3)) %>%
  dplyr::select(-both_country)

#vote_summ$from_country[5] <- "Albania"
#vote_summ$to_country[5] <- "Belarus"
```

# long/lat join df for from_country
```{r}
country_join_a <- df %>%
  dplyr::select(from_country = iso3, x, y)
```

# long/lat join df for to_country
```{r}
country_join_b <- df %>%
  dplyr::select(to_country = iso3,x,y) %>% 
  rename(xend = x,
         yend = y)
```

```{r}
# create df for plotting with both sets of long/lat values
plot_df <- data.frame(from_country = rownames(vote_mat)) %>%
  inner_join(vote_summ, by = "from_country") %>%
  inner_join(country_join_a, by = c("from_country")) %>%
  inner_join(country_join_b, by = c("to_country")) %>%
  dplyr::select(-to_country, country = from_country) %>%
  arrange(points)

```

# create top 5 section:

```{r}
top_table <- vote_summ %>%
  arrange(-points) %>%
  head(10) %>%
  mutate(rank = 1:10)
```

# function to get Eurovision logo file

SKIP THIS FOR NOW

```{r}
get_png <- function(filename) {
  grid::rasterGrob(png::readPNG(filename), interpolate = TRUE)
}
```

```{r}
# save logo file
logo <- get_png("2022 Week 20 - Eurovision/img/Eurovision_generic_white.png")
```

# create simple world map

```{r}
map <- map_data("world") %>% 
  dplyr::select(x = long, y = lat, group, id = subregion) %>%
  mutate(xend = 0,
         yend = 0)
```


# build plot

```{r}
ggplot(plot_df, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_polygon(data = map, aes(group = group), fill = "#231f36", colour = "#2d2942") +
  geom_edges(aes(alpha = (points ^ 2), size = (points ^ 3), color = points), curvature = -0.1) +
  geom_nodes(size = 10, color = "#1c192c", alpha = 0.8) +
  geom_nodetext(aes(label = str_wrap(toupper(country), 8)), family = "Rubik", size = 2.5, color = "white",
                fontface = "bold") #+
  geom_text(x = -20, y = 70, hjust = 0, color = "white", size = 7, family = "Rubik", label = "Eurovision's Strongest International Bonds") +
  geom_text(x = -20, y = 68.7, hjust = 0, color = "white", size = 3.2, family = "Rubik", label = "Average points awarded between nations in Eurovision Grand Finals from 1975-2022") +
  geom_text(x = 50, y = 30, hjust = 0.8, color = "white", angle = 25, size = 2.5, family = "Rubik", label = "AUSTRALIA") +
  geom_text(x = 42, y = 71, hjust = 0.5, color = "white", size = 3, family = "Rubik", fontface = "bold",  label = "Top 10 country pairs by avg. points awarded") +
  geom_point(data = top_table, aes(x = 42, y = 71 - (rank / 1), xend = NULL, yend = NULL, color = points, size = (points ^ 3) + 20)) +
  geom_text(data = top_table, aes(x = 42, y = 71 - (rank / 1), xend = NULL, yend = NULL, label = round(points, 1)), size = 2, family = "Rubik", fontface = "bold", color = "#1c192c") + # points number text
  geom_text(data = top_table, aes(x = 41, y = 71 - (rank / 1), xend = NULL, yend = NULL, label = toupper(to_country)), hjust = 1, color = "white", size = 2.5) + # left country
  geom_text(data = top_table, aes(x = 43, y = 71 - (rank / 1), xend = NULL, yend = NULL, label = toupper(from_country)), hjust = 0, color = "white", size = 2.5) + # right country
  scale_color_viridis_b() +
  guides(size = "none", alpha = "none") +
  labs(color = "", caption = "Country pairings with fewer than 10 points exchanges are not shown.\ndata: Eurovision / Data.World", x = "average points awarded") +
  # ggtitle("THE POLITICS OF EUROVISION") +
  theme_blank() +
  coord_cartesian(xlim = c(-20, 50), ylim = c(30,70)) +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(),
    legend.key.width = unit(2, "cm"),
    legend.key.height = unit(0.1, "cm"),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.background = element_rect(fill = "#1c192c", color = "#1c192c"),
    panel.background = element_rect(fill = "#1c192c", color = "#1c192c"),
    text = element_text(family = "Rubik", color = "white"),
    legend.background = element_rect(fill = "#1c192c"),
    legend.margin = margin(t = -0.3, unit = "cm")
  )
```

