---
title: "Untitled"
author: "Caitie"
date: "19/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(data.table)
library(countrycode)
library(raster)
library(sf)
```
# Load data

```{r}
basin_table<-read.csv(here("results/Basin_results_table.csv"))
iso3_table<-read.csv(here("results/Country_terrestrial_results_table.csv"))
continent_table<-read.csv(here("results/Continent_terrestrial_results_table.csv"))
```

# Results

Number of basins in analysis

```{r}
length(unique(basin_table$MAIN_BAS))
```
Number/proportion that are transboundary
```{r}
trans_basins<-basin_table %>% 
  filter(n_iso3>1)

length(unique(trans_basins$MAIN_BAS))
length(unique(trans_basins$MAIN_BAS))/length(unique(basin_table$MAIN_BAS))
```

Proportion of transboundary by continent
```{r}
continent_table %>% 
  dplyr::select(Continent, prop_trans) %>% 
  arrange(desc(prop_trans))
  
```
# Country basin results

Number of countries in analysis
```{r}
length(unique(iso3_table$ISO3))
```
Number of countries with transboundary basins

```{r}
trans_country<-iso3_table %>% 
  filter(!is.na(n_trans_basin) == T)

length(unique(trans_country$ISO3))
length(unique(trans_country$ISO3))/length(unique(iso3_table$ISO3))
```

Countries with all transboundary basins
```{r}
iso3_table %>% 
  filter(prop_trans == 1) %>% 
  nrow()
```

```{r}
iso3_table %>% 
  filter(prop_trans == 1) %>% 
  nrow()/length(unique(iso3_table$ISO3))
```
Countries with all transboundary cryptorheic
```{r}
iso3_table %>% 
  filter(prop_trans_crypt == 1) %>% 
  nrow()
```

```{r}
iso3_table %>% 
  filter(prop_trans_crypt == 1) %>% 
  nrow()/length(unique(iso3_table$ISO3))
```

# Sediment results

Total sediment exported globally (megatonnes)
```{r}
sum(basin_table$total_sed_bas, na.rm = T)/1000000
```
Transboundary sediment export
```{r}
basin_table %>% 
  filter(n_iso3 >1) %>% 
  summarise(.,sum(total_sed_bas, na.rm = T))/1000000
```
```{r}
basin_table %>% 
  filter(n_iso3 >1) %>% 
  summarise(.,sum(total_sed_bas, na.rm = T))/sum(basin_table$total_sed_bas, na.rm = T)
```

Continent results

```{r}
continent_table %>% 
  dplyr::select(Continent, prop_trans_sed) %>% 
  arrange(desc(prop_trans_sed))
```

Country results

```{r}
test<-iso3_table %>% 
  filter(prop_trans_sed == 1)
```

# Transboundary mismatch

Mismatch in where the sediment comes form and where the pourpoint is

At this point we don't care whether it is cryptoheric or not

```{r}
list_mismatch<-list.files(here("output_data/Transboundary"), pattern = "Terrestrial", full.names = T)
  
mismatch<-do.call(rbind,
          lapply(list_mismatch, read.csv))

```

Mismatch between country that produces majority of sediment and where sediment is released
```{r}
sub_mismatch<-mismatch %>% 
  filter(!pp_iso3 == "character(0)",
    max_sed_iso3 != pp_iso3,
          nchar(pp_iso3)==3)

length(unique(sub_mismatch$MAIN_BAS))
```

```{r}
sub_mismatch %>% 
  group_by(Continent) %>% 
  summarise(uniq_bas = length(unique(MAIN_BAS)),
            prop_bas = uniq_bas/length(unique(sub_mismatch$MAIN_BAS)))

table(sub_mismatch$Continent)/length(unique(sub_mismatch$MAIN_BAS))
```

Mismatches where >90% of sediment is produced in the country that does not contain the pourpoint

Potentially modify if we don't want rivers with no discharge.
```{r}
maj_sub_mismatch<-sub_mismatch %>% 
  filter(prop_sed>0.9)

length(unique(maj_sub_mismatch$MAIN_BAS))
```


```{r}
maj_sub_mismatch %>% 
  group_by(ISO3) %>% 
  summarise(uniq_bas = length(unique(MAIN_BAS)),
            prop_bas = uniq_bas/length(unique(maj_sub_mismatch$MAIN_BAS))) %>% 
  arrange(desc(prop_bas))
```


If we remove rivers without discharge it is

```{r}
sub_mismatch2<-sub_mismatch %>% 
  filter(rv_d_3_>0,
         !is.na(rv_d_3_) == T,
    max_sed_iso3 != pp_iso3)

length(unique(sub_mismatch2$MAIN_BAS))
```
Check these basins:
7080073410 Seems weird as multiple countries but they are small islands

Check ones that have charachter(0) as pp_loc

1080020200 in Africa but does not have Pp location - remove?
2080000360 Same as above in Asia
2080006710 Same as above
2080019300
2080022590
2080069200
4080002770

These seem to not have pourpoint locations - so for now I remove them.


Additional areas of concern - but the same proportion of pourpoints across multiple countries
```{r}
equal_pp<-mismatch %>% 
  filter(nchar(pp_iso3)>3)
```


# Transboundary, cryptoheric watersheds

Pourpoint locations

```{r}
pp_loc_list<-list.files(here("output_data/Pourpoints"), pattern = "Missing_pp_chunk", full.names = T)

pp_loc_mis<-
  do.call(rbind,
          lapply(pp_loc_list, read.csv))

pp_all<-read.csv(here("output_data/Pourpoints/PP_location_all.csv"))

pp_done<-rbind(pp_all, pp_loc_mis) %>% 
  dplyr::select(HYRIV_I, NEXT_DO, MAIN_RI, rv_d_3_, ENDORHE, MAIN_BAS)
```

Join to sed dat

Number of cryptorheic basins
```{r}
crypt<-full_join(sed_dat, pp_done, by = "MAIN_BAS") %>% 
  filter(ENDORHE == 0)

length(unique(crypt$MAIN_BAS))/23934
```

Number of transboundary cryptoheric basins

```{r}
trans_crypt<-crypt %>% 
  filter(MAIN_BAS %in% trans_basins$MAIN_BAS) # DOUBLE CHECK THIS

length(unique(trans_crypt$MAIN_BAS))
length(unique(trans_crypt$MAIN_BAS))/length(unique(trans_basins$MAIN_BAS))
```

Remove rivers with  no discharge - need to see what to do about these
```{r}
sub_trans_crypt<-crypt %>% 
  filter(MAIN_BAS %in% trans_basins$MAIN_BAS,
         rv_d_3_>0)

length(unique(sub_trans_crypt$MAIN_BAS))
length(unique(sub_trans_crypt$MAIN_BAS))/length(unique(trans_basins$MAIN_BAS))
```
```{r}
trans_crypt_df<-trans_crypt %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)


trans_crypt_df %>% 
  group_by(Continent) %>% 
  summarise(uniq_bas = length(unique(MAIN_BAS)),
            prop_bas = uniq_bas/length(unique(trans_crypt$MAIN_BAS))) %>% 
  arrange(desc(prop_bas))
```
```{r}
trans_crypt_sed<-sed_dat %>% 
  filter(MAIN_BAS %in% trans_crypt$MAIN_BAS)

sum(trans_crypt_sed$sed_sum,na.rm = T)/1000000
sum(trans_crypt_sed$sed_sum,na.rm = T)/total_sed
```


# Transboundary coral reef sediments

DOUBLE CHECK THIS - make sure using right pourpoint layer

```{r}
# These pourpoints are just ones that drain to coral reefs? Double check
reef_pp<-st_read(here("raw_data/Pourpoints/pour_points_all.shp")) 

reef_sed<- trans_crypt_df %>% 
  filter(HYRIV_I %in% reef_pp$HYRIV_I)
```

```{r}
length(unique(reef_sed$MAIN_BAS))
length(unique(reef_sed$MAIN_BAS))/length(unique(trans_crypt_sed$MAIN_BAS))
```

```{r}
sum(reef_sed$sed_sum, na.rm = T)/sum(trans_crypt_sed$sed_sum, na.rm = T)

sum(reef_sed$sed_sum, na.rm = T)/sum(trans_sed_sum$sed_sum, na.rm = T)

sum(reef_sed$sed_sum, na.rm = T)/total_sed
```

# EEZ results

## Total sediment plumed

## EEZ Mismatch

```{r}
eez_mismatch<-read.csv(here("output_data/EEZ_sediments/EEZ_sed_trans_mismatch.csv"))

iso3_eez_mismatch<-eez_mismatch %>% 
  mutate(Sink_ISO3 = ifelse(Sink_ISO3 == " ", Sink_SOVISO3, Sink_ISO3)) %>% 
  group_by(Sink_ISO3, Sink_name, Source_ISO3) %>% 
  summarise(shared_sed = sum(total_eez_sed, na.rm = T),
            source_sed = sum(unique(Source_sediment), na.rm = T),
            prop = shared_sed/source_sed) %>% 
  dplyr::select(Source_ISO3, Sink_ISO3, shared_sed, source_sed, prop, Sink_name)
```

# Countries that trade sediment back and forth

```{r}
test<-iso3_eez_mismatch %>% 
  mutate(c = stringr::str_c(Sink_ISO3, Source_ISO3),
         d = stringr::str_c(Source_ISO3, Sink_ISO3))

test2<-iso3_eez_mismatch %>% 
  mutate(c = stringr::str_c(Source_ISO3, Sink_ISO3))

test3<-test %>% 
  filter(c %in% test$c)

cat<-unique(test3$c)

combo_all<-c()

for(i in 1:length(cat)){
  
  sub1<-test3 %>% 
    filter(c == cat[[i]])
  
  sub2<-test3 %>% 
    filter(d == cat[[i]])
  
  c1<-sub1$Source_ISO3
  c2<-sub1$Sink_ISO3
  
  combo<-data_frame(x = c1, y = c2, sed_from_x = sub1$shared_sed, sed_from_y = sub2$shared_sed, sed_total_x = sub1$source_sed, sed_total_y = sub2$source_sed, name_x = sub1$Sink_name, name_y = sub2$Sink_name)
  
  combo_all<-rbind(combo_all, combo)
}

test<-combo_all %>% 
  filter(x != y)

test<-unique(iso3_eez_mismatch$Source_ISO3)
test2<- unique(iso3_eez_mismatch$Sink_ISO3)

test3<-test[test %in% test2]
test4<-test2[test2 %in% test]
```


## Places with both transboundary terrestrial basin and transboundary EEZ?? Potential starts in Spain, pour point in France but plumes back to spain???