---
title: "Untitled"
author: "Caitie"
date: "09/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(data.table)
library(countrycode)
library(raster)
library(sf)

options(scipen = 999)
```

# Load data

## Proportion basins in each country

Number of basins per country
```{r}
list_prop_basin<-list.files(here("output_data"), pattern = "Prop_basin_iso3", full.names = TRUE)

sub_prop_basin<-list_prop_basin[grep(list_prop_basin, pattern = ".csv")] 

dat <- 
  do.call(rbind,
          lapply(sub_prop_basin, read.csv))

```

## Sediment export

# Sediment export

```{r}
# Total sediment exported
#sed_moll<-raster(here("raw_data/Sediment/sediment_export_global_moll.tif"))

#total_sed<-cellStats(sed_moll, "sum")

total_sed<-24849341974

# unit is tonnes/ha/yr
#1 Mt = 1000000 t

#Estimated ha of global basins = 13511831300

total_sed_mt<-total_sed/1000000 #Megaton

total_sed_mt
```

## Sediment export

```{r}
list_sed_basin<-list.files(here("output_data/Sediment"), pattern = ".shp", full.names = T)

sed_dat <- 
  do.call(rbind,
          lapply(list_sed_basin, st_read))

```

## Pourpoint locations

```{r}
pp_loc_list<-list.files(here("output_data/Pourpoints"), pattern = "Missing_pp_chunk", full.names = T)

pp_loc_mis<-
  do.call(rbind,
          lapply(pp_loc_list, read.csv))

pp_all<-read.csv(here("output_data/Pourpoints/PP_location_all.csv"))

pp_done<-rbind(pp_all, pp_loc_mis) %>% 
  dplyr::select(HYRIV_I, NEXT_DO, MAIN_RI, rv_d_3_, ENDORHE, MAIN_BAS)
```


# Terrestrial Transboundary table

## Basin results

Number of countries per basin

```{r}
n_iso3_basin<-dat %>% 
  group_by(MAIN_BAS) %>% 
  summarise(n_iso3 = length(unique(ISO3)))
```

Total sediment per basin

```{r}
basin_sed_dat<-sed_dat %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(total_sed_bas = sum(sed_sum, na.rm = T)) %>% 
  mutate(prop_sed = total_sed_bas/total_sed)

#test<-sed_dat %>% 
#  filter(MAIN_BAS == 1080000520)
```

```{r}
basin_table<-full_join(n_iso3_basin, basin_sed_dat)
```

Cryptorheic basins

```{r}
crypt_basins<-pp_done %>% 
  filter(ENDORHE == 0)
```

```{r}
basin_table<-basin_table %>% 
  mutate(crypt = ifelse(MAIN_BAS %in% crypt_basins$MAIN_BAS, 1, 0))
```

```{r}
write.csv(basin_table, here("results/Basin_results_table.csv"))
```

## Country results
Number of basins per country

```{r}
n_basin_iso3<-dat %>% 
  group_by(ISO3) %>% 
  summarise(n_basin = length(unique(MAIN_BAS)))
```

Number of transboundary basins per country

```{r}
trans_basins<-basin_table %>% 
  filter(n_iso3 >1)

n_basin_iso3_trans<- dat %>% 
  filter(MAIN_BAS %in% trans_basins$MAIN_BAS) %>% 
  group_by(ISO3) %>% 
  summarise(n_trans_basin = length(unique(MAIN_BAS)))
```

Number of cryptorheic basins per country

```{r}
crypt_basins<-basin_table %>% 
  filter(crypt == 1)

n_crypt_basins_iso3<-dat %>% 
  filter(MAIN_BAS %in% crypt_basins$MAIN_BAS) %>% 
  group_by(ISO3) %>% 
  summarise(n_crypt_basin = length(unique(MAIN_BAS)))
```

Number of transboundary cryptorheic basins

```{r}
n_trans_crypt_basins_iso3<-dat %>% 
  filter(MAIN_BAS %in% trans_basins$MAIN_BAS,
    MAIN_BAS %in% crypt_basins$MAIN_BAS) %>% 
  group_by(ISO3) %>% 
  summarise(n_trans_crypt_basin = length(unique(MAIN_BAS)))
```

Proportion transboundary basins
Proprotion of cryptorheic basins
Proportion transboundary cryptorheic basins
```{r}
iso3_basins<-full_join(n_basin_iso3, n_basin_iso3_trans) %>% 
  full_join(., n_crypt_basins_iso3) %>% 
  full_join(., n_trans_crypt_basins_iso3) %>% 
  mutate(prop_trans = n_trans_basin/n_basin,
         prop_crypt = n_crypt_basin/n_basin,
         prop_trans_crypt = n_trans_crypt_basin/n_basin)
```
Total sediment per country

```{r}
iso3_sed<-sed_dat %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  group_by(ISO3) %>% 
  summarise(sed_iso3 = sum(sed_sum, na.rm = T))
```

Total transboundary sediment per country

```{r}
trans_iso3_sed<-sed_dat %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  filter(MAIN_BAS %in% trans_basins$MAIN_BAS) %>% 
  group_by(ISO3) %>% 
  summarise(trans_sed_iso3 = sum(sed_sum, na.rm = T))
```

Total cryptorheic sediment

```{r}
crypt_iso3_sed<-sed_dat %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  filter(MAIN_BAS %in% crypt_basins$MAIN_BAS) %>% 
  group_by(ISO3) %>% 
  summarise(crypt_sed_iso3 = sum(sed_sum, na.rm = T))
```

Total transboundary cryptorheic sediment

```{r}
trans_crypt_iso3_sed<-sed_dat %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  filter(MAIN_BAS %in% trans_basins$MAIN_BAS,
    MAIN_BAS %in% crypt_basins$MAIN_BAS) %>% 
  group_by(ISO3) %>% 
  summarise(trans_crypt_sed_iso3 = sum(sed_sum, na.rm = T))
```

Proportion transboundary sediment
Proportion cryptorheic sediment
Proportion transboundary cryptorheic sediment

```{r}
iso3_basins_sed<-full_join(iso3_sed, trans_iso3_sed) %>% 
  full_join(., crypt_iso3_sed) %>% 
  full_join(., trans_crypt_iso3_sed) %>% 
  mutate(prop_trans_sed = trans_sed_iso3/sed_iso3,
         prop_crypt_sed =crypt_sed_iso3/sed_iso3,
         prop_trans_crypt_sed = trans_crypt_sed_iso3/sed_iso3)
```

```{r}
iso3_table<-full_join(iso3_basins, iso3_basins_sed)
```

```{r}
write.csv(iso3_table, here("results/Country_terrestrial_results_table.csv"))
```


