---
title: "Terrestrial_trans_mismatch"
author: "Caitie"
date: "03/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(sf)

t_crs<-'ESRI:54009'
```

# Load data

Proportin of basin in each country
```{r}
files<-list.files(path = here("output_data"), pattern = "Prop_basin_iso3_", full.names = T)

sub_files<-files[grep(pattern = ".csv", files)]
sub_files<-sub_files[-2] #Remove Antarctica

basin_iso3_files<-files[grep(pattern = ".shp", files)]

shp_files<-list.files(path = here("output_data/Sediment"), pattern = ".shp", full.names = T)
```

```{r}
basins<-st_read(here("output_data/Basins/Basins_lv8_mainbasin_moll.shp")) %>% 
  st_make_valid() 
```

# PP Location

```{r}
pp_loc_list<-list.files(here("output_data/Pourpoints"), pattern = "Missing_pp_chunk", full.names = T)

pp_loc_mis<-
  do.call(rbind,
          lapply(pp_loc_list, read.csv))

pp_all<-read.csv(here("output_data/Pourpoints/PP_location_all.csv"))

pp_done<-rbind(pp_all, pp_loc_mis)
```

# Sediment at pourpoints

```{r}
pp_sed_all<-st_read(here(paste0("output_data/Sediment_at_pourpoint/Sediment_at_pourpoint.shp")))
```
```{r}
pp_sed_join<-full_join(pp_sed_all, pp_done)
```

# Function to find mismatch

2080092790 in Iran and Afghanistan

Check ones that have charachter(0) as pp_loc

1080020200 in Africa but does not have Pp location - remove?
2080000360 Same as above in Asia
2080006710 Same as above
2080019300
2080022590
2080069200
4080002770

```{r}
land_trans_sed<-function(x){
  
  # Read in proportion of basin csv for country and subset to transboundary basins
  dat<-read.csv(x) %>% 
    filter(n>1)
  
  # Get name for matching
  name<-str_remove(x, here("output_data/Prop_basin_iso3_"))
  name2<-str_remove(name, ".csv")
  
  # Match to sediment calculation shapefile for country
  sub_shp<-shp_files[grep(pattern = name2, shp_files)]
  # Read in sediment file
  sed_dat<-st_read(sub_shp) %>% 
  dplyr::select(ISO3, Country, MAIN_BAS, Continent, sed_sum, sed_mean) %>% 
    st_transform(., t_crs)
  
  # Join sediment data to proportion of basin data
  sed_basin<-right_join(sed_dat, dat, by = c("MAIN_BAS", "Country", "ISO3", "Continent")) 
  
  # Calculate total sediment by main basin
  total_sed<-sed_dat %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(total_sed = sum(sed_sum, na.rm = T))
  
  # Join total sediment to sediment data to calculate proportion of sediment per country/basin
  sed_basin<-sed_basin %>% 
  full_join(., total_sed, by = "MAIN_BAS") %>% 
  mutate(prop_sed = sed_sum/total_sed)
  
  # Read in pourpoint location data
 
  pp_sed<-pp_sed_join %>% 
    filter(Continent == name2)
  
  #bas<-unique(pp_sed$MAIN_BAS)
  
  sed_basin2<-sed_basin %>% 
    filter(!is.na(ISO3) == T)
  
  bas<-unique(sed_basin2$MAIN_BAS)
  
  test<-pp_sed %>% 
    filter(pp_sed$MAIN_BAS %in% sed_basin2$MAIN_BAS)

  all<-c()

for(i in 1:length(bas)){
  
  print(i)
  
  sub<-sed_basin2 %>% 
    filter(MAIN_BAS == 	bas[i]) %>% 
    as.data.frame() %>% 
    dplyr::select(-geometry) %>% 
    mutate(prop_basin = round(prop_basin, 3))
  
  test_sed<-sum(sub$sed_sum,na.rm = T)
  
  #If no sediment exported from basin we skip it
  #I think this only occurs for MAIN_BAS 2080084740 in Asia
  if(test_sed == 0){ 
    next()
  }
  
  sub_pp<-pp_sed %>% 
    filter(MAIN_BAS == bas[i]) %>% 
    as.data.frame() %>% 
    dplyr::select(-geometry) %>% 
    dplyr::select(HYRIV_I, ISO3, NEXT_DO, MAIN_RI, rv_d_3_, ENDORHE, MAIN_BAS, Continent)
  
  sub_pp2<-unique(sub_pp$HYRIV_I) #assume NAs mean there is only 1 pp in basin
  
  sub_pp2<-sub_pp2[!is.na(sub_pp2) == T]
  
  pp_num<- length(sub_pp2)
  
  pp_prop <- sub_pp %>% 
    group_by(MAIN_BAS, ISO3) %>% 
    mutate(n_pp = length(unique(HYRIV_I)),
           total_pp = pp_num,
           n_pp = ifelse(is.na(HYRIV_I) == T, 0, as.numeric(n_pp)),
           prop_pp = n_pp/pp_num)
  
  total_discharge <- sub_pp %>% 
    group_by(MAIN_BAS) %>% 
    summarise(total_discharge = sum(rv_d_3_, na.rm = T))
  
  sub_pp3 <- sub_pp %>% dplyr::select(-ISO3, -Continent)
  
  sed_discharge<- sub %>% 
    full_join(., sub_pp3, by = c("MAIN_BAS")) %>% 
    full_join(., total_discharge) %>% 
    mutate(prop_dis = rv_d_3_/total_discharge,
           pp_dis = prop_dis * total_sed * prop_sed)
  
  pp_loc<-unique(pp_prop[which(pp_prop$prop_pp == max(pp_prop$prop_pp)), "ISO3"])
  
 maj_dis<-sed_discharge %>% 
    group_by(ISO3, MAIN_BAS) %>% 
    summarise(iso3_pp_dis = sum(pp_dis, na.rm = T)) %>% 
    mutate(iso3_pp_dis_prop = iso3_pp_dis/unique(sub$total_sed))
  
  maj_dis_loc<-maj_dis %>% 
    filter(iso3_pp_dis_prop == max(maj_dis$iso3_pp_dis_prop)) %>% 
    dplyr::select(ISO3) %>% 
    as.character()
  
  max_sed<-max(sub$prop_sed,na.rm = T)
  maj_sed<-unique(sub[which(sub$prop_sed == max_sed), "ISO3"])
  max_bas<-max(sub$prop_basin,na.rm = T)
  maj_prop<-unique(sub[which(sub$prop_basin == max_bas), "ISO3"])
  n_iso3 <-length(unique(sub$ISO3))
  
  done<-pp_prop %>% 
    full_join(., sed_discharge) %>% 
    dplyr::select(ISO3, MAIN_BAS, Continent, sed_sum, sed_mean, area_km2, b_area_km2, iso3_b_km2, prop_basin, n, total_sed, prop_sed, HYRIV_I, rv_d_3_, ENDORHE, n_pp, total_pp, prop_pp, prop_dis, pp_dis) %>% 
    mutate(pp_iso3 = as.character(pp_loc),
           max_pp_dis_iso3 = maj_dis_loc,
           max_sed_iso3 = maj_sed,
           max_prop_bas_iso3 = maj_prop,
           iso3_pp_dis_prop = pp_dis/unique(sub$total_sed),
           n_iso3 = n_iso3) 
  
  all<-rbind(all, done)
}
  
   missing_pp_basins<-dat[which(!dat$MAIN_BAS %in% pp_sed$MAIN_BAS),]
   write.csv(missing_pp_basins, here(paste0("output_data/Pourpoints/Missing_basins_pp_", name2,".csv")))
   write.csv(all, here(paste0("output_data/Transboundary/Terrestrial_transboundary_",name2,".csv")))
}
```



```{r}
pbmclapply(sub_files, land_trans_sed, mc.cores = length(sub_files), mc.style = "ETA")
```

# Missing basins explanations

Africa
1080018110 - no pourpoint located in this basin - differences between RiverAtlas and Country/Sediment layers
1080020200 - no pourpoint located in this basin - differences between RiverAtlas and Country/Sediment layers


Asia - there are 6

Europe there are 3
Oceania there are 2
North America 3
South America 0 

```{r}
name2<-"South America"
test<-read.csv(here(paste0("output_data/Pourpoints/Missing_basins_pp_", name2,".csv")))
length(unique(test$MAIN_BAS))
```

